Intelligent Building Energy Management System

### 2021-05-08 parts/20-iBEMSArchitecture.tex
Updated file paths and added figures
Updated figs
Updated report

At the center of the iBEMS architecture is the iBEMS core. This core interacts
with multiple peripherals including IoT devices and a weather API over the
internet. Over the course of this project, we managed to develop support for 2
IoT devices displayed in Figure~\ref{fig:highLevelArchitecture}. %
%
\begin{figure}
  \centering
  \includegraphics[scale=0.3]{figs/highLevelArchitecture.pdf}
  \caption{High Level Architecture of the Proposed System}
  \label{fig:highLevelArchitecture}
\end{figure}
%
These devices are the WeMo Insight Switch and an embedded computer known as the Beaglebone
Blue. Our initial plan for the smart meter shown in
Figure~\ref{fig:highLevelArchitecture} was to use it in a Simscape model of a
microgrid. However, we did not list this as a requirement for the project, so we
decided not to implement it due to time constraints. The core is also able to
connect the internet to download weather data for Peoria, Illinois through
OpenWeatherMap.

@@

A large feature of this project was being able to record power usage from the
connected IoT devices. The embedded computer does not have a built-in capability
to measure its own power usage, so a circuit was needed to make that
possible. Essentially, this circuit will measure the current being used to drive
one of the motors on the robot chassis. The on-board Analog-to-Digital-Converter
(ADC) can be used to read the voltage across the resistor and since the
resistance is known, the current can be calculated as $I = V/R$. Also, the
voltage from the H-Bridge to drive the motors on the embedded computer is known
so the power consumed by 1 motor is $Motor Drive Voltage * I$. For the specific
robot chassis used in this project, there are 4 motors, so multiplying the power
found from this circuit by 4 will give an approximation of the total power used
by the robot. \add{For other robots with different power sources besides a Lipo
battery.} See Figure~\ref{fig:motorInterfaceCircuit} for details of the interface
circuit for computer power usage by the DC motor.

\begin{figure}
  \centering
  \begin{circuitikz}[american]
    \tikzstyle{every node} = [font = \tiny]
    % \usetikzlibrary{patterns}
    \draw
    (0,0) to[sqV,invert,l=Motor Drive Voltage from H-Bridge] ++(0,4*\smgrid)
    to[Telmech=M,n=motor,fill=red!20] ++(4*\smgrid,0)
    to[C,l=$1~{[}\mu F{]}$,*-*] ++(0,-4*\smgrid) to[short]++(-4*\smgrid,0); 
    \draw
    (4*\smgrid,4*\smgrid) to[short,-*]++(3*\smgrid,0)
    to[short,-o]++(2*\smgrid,0)node[right]{Embedded Computer ADC (Ch\#0)};
    \draw
    (7*\smgrid,4*\smgrid) to[R,l=$2~{[}\Omega{]}$,-*]++(0,-4*\smgrid)
    to[short]++(-4*\smgrid,0);
    \draw
    (7*\smgrid,0) to[short,-o]++(2*\smgrid,0) node[right]{Embedded
      Computer ADC (Ground)};
  \end{circuitikz}
  \caption{Interface circuit to calculate power consumption of a DC motor
    running from the embedded computer copmuter.}
  \label{fig:motorInterfaceCircuit}
\end{figure}

% \pagebreak
\begin{figure}[H]
    \centering
    \includegraphics[scale=0.1]{figs/notConnectedSBC.jpg}
    \caption{Embedded Computer Not Connected}
    \label{fig:not_connected_bb}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[scale=0.1]{figs/connectedSBC.jpg}
    \caption{Embedded Computer Connected}
    \label{fig:connected_bb}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[scale=0.085]{figs/wemoView.jpg}
    \caption{WeMo Insight Smart Plug}
    \label{fig:wemo}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[scale=0.1]{figs/overallView.jpg}
    \caption{Overall View}
    \label{fig:overallView}
\end{figure}

>>>>

At the center of the iBEMS architecture is the iBEMS core. This core interacts
with multiple peripherals including IoT devices and a weather API over the
internet. Over the course of this project, we managed to develop support for 2
IoT devices displayed in Figure~\ref{fig:highLevelArchitecture}. %
%
\begin{figure}[H]
  \centering
  \includegraphics[scale=0.3]{figs/overallConnectionDiagram.pdf}
  \caption{High Level Architecture of the Proposed System}
  \label{fig:highLevelArchitecture}
\end{figure}
%
These devices are the WeMo Insight Switch and an embedded computer known as the Beaglebone
Blue. Our initial plan for the smart meter shown in
Figure~\ref{fig:highLevelArchitecture} was to use it in a Simscape model of a
microgrid. However, we did not list this as a requirement for the project, so we
decided not to implement it due to time constraints. The core is also able to
connect the internet to download weather data for Peoria, Illinois through
OpenWeatherMap.

@@

A large feature of this project was being able to record power usage from the
connected IoT devices. The embedded computer does not have a built-in capability
to measure its own power usage, so a circuit was needed to make that
possible. Essentially, this circuit will measure the current being used to drive
one of the motors on the robot chassis. The on-board Analog-to-Digital-Converter
(ADC) can be used to read the voltage across the resistor and since the
resistance is known, the current can be calculated as $I = V/R$. Also, the
voltage from the H-Bridge to drive the motors on the embedded computer is known
so the power consumed by 1 motor is $Motor Drive Voltage * I$. For the specific
robot chassis used in this project, there are 4 motors, so multiplying the power
found from this circuit by 4 will give an approximation of the total power used
by the robot. See Figure~\ref{fig:motorInterfaceCircuit} for details of the interface
circuit for computer power usage by the DC motor. Also see Figure~\ref{fig:bb_connections} for how the circuit is connected to the embedded computer and robot chassis.

\begin{figure}[H]
  \centering
  \begin{circuitikz}[american]
    \tikzstyle{every node} = [font = \tiny]
    % \usetikzlibrary{patterns}
    \draw
    (0,0) to[sqV,invert,l=Motor Drive Voltage from H-Bridge] ++(0,4*\smgrid)
    to[Telmech=M,n=motor,fill=red!20] ++(4*\smgrid,0)
    to[C,l=$1~{[}\mu F{]}$,*-*] ++(0,-4*\smgrid) to[short]++(-4*\smgrid,0); 
    \draw
    (4*\smgrid,4*\smgrid) to[short,-*]++(3*\smgrid,0)
    to[short,-o]++(2*\smgrid,0)node[right]{Embedded Computer ADC (Ch\#0)};
    \draw
    (7*\smgrid,4*\smgrid) to[R,l=$2~{[}\Omega{]}$,-*]++(0,-4*\smgrid)
    to[short]++(-4*\smgrid,0);
    \draw
    (7*\smgrid,0) to[short,-o]++(2*\smgrid,0) node[right]{Embedded
      Computer ADC (Ground)};
  \end{circuitikz}
  \caption{Interface circuit to calculate power consumption of a DC motor
    running from the embedded computer copmuter.}
  \label{fig:motorInterfaceCircuit}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[scale=0.6]{figs/beaglebone/connections.pdf}
    \caption{Connections between Embedded Computer, circuit, and robot chassis}
    \label{fig:bb_connections}
\end{figure}

% \pagebreak
\begin{figure}[H]
    \centering
    \includegraphics[scale=0.07]{figs/beaglebone/notConnectedSBC.jpg}
    \caption{Embedded Computer Not Connected}
    \label{fig:not_connected_bb}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[scale=0.07]{figs/beaglebone/connectedSBC.jpg}
    \caption{Embedded Computer Connected}
    \label{fig:connected_bb}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[scale=0.07]{figs/wemo/wemoView.jpg}
    \caption{WeMo Insight Smart Plug}
    \label{fig:wemo}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[scale=0.07]{figs/overallView.jpg}
    \caption{Overall View}
    \label{fig:overallView}
\end{figure}
